---
title: "Activity 2 - Day 1"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(tidymodels)
```

```{r}
data <- read_csv("hfi.csv")
```


```{r}
head(data)
```


```{r}
readr::read_csv("https://www.openintro.org/data/csv/hfi.csv")
```


```{r}
hfi <- read_csv("https://www.openintro.org/data/csv/hfi.csv")
```


```{r}
hfi
```
# 1. What are the dimensions of the dataset? What does each row represent? #



```{r}
dim(hfi)
```

We can see from the above code that the dimension of the hfi dataset is 1458 observations and 123 variables.

As we are only concerned about the year 2016:
```{r}
hfi_2016 <- subset(hfi, year == 2016)
```

After selecting only the year 2016, we get that the dimension of the hfi_2016 is 162 obervation and 123 variables.

# 2. What type of plot would you use to display the relationship between the personal freedom score, pf_score, and pf_expression_control? #

I would use scatter plot to display the relationship between the pf_score and pf_expression_control as below:


```{r}
plot(hfi_2016$pf_score ~ hfi_2016$pf_expression_control,
     xlab = "Expression control", ylab = "Pf Score", col = "red")
```


# 3. Does the relationship look linear? If you knew a country’s pf_expression_control, or its score out of 10, with 0 being the most, of political pressures and controls on media content, would you be comfortable using a linear model to predict the personal freedom score? #

yes, I feel the relationship looks **linear** as with the increase in the expression control, the pf_score increases too. 

#Task 4: Sum of squared residuals #

# 4. Using openintro::plot_ss, choose a line that does a good job of minimizing the sum of squares. Run the function several times. What was the smallest sum of squares that you got? How does it compare to your neighbour’s? #

After running the sum of square multiple times, the smallest number of sume of square I got was 108.484


# Task 5: The Linear Model #

```{r}
m1 <- lm(pf_score ~ pf_expression_control, data = hfi_2016)
m1
tidy(m1)
```

```{r}
summary(m1)
```

# 5. Interpret the y - intercept #

The y-intercept is 4.2838. So, the human freedom score with no amount of political pressure on media is 4.2838.

# 6. Interpret the slope # 

The slope here is 0.5419. So, for each additional amount of the pressure on media content score, we would see the human freedom score to increase by 0.5419. 
