---
title: "Activity 2 - Day 1"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(tidymodels)
```

```{r}
data <- read_csv("hfi.csv")
```


```{r}
head(data)
```


```{r}
readr::read_csv("https://www.openintro.org/data/csv/hfi.csv")
```


```{r}
hfi <- read_csv("https://www.openintro.org/data/csv/hfi.csv")
```


```{r}
hfi
```
# 1. What are the dimensions of the dataset? What does each row represent? #



```{r}
dim(hfi)
```

We can see from the above code that the dimension of the hfi dataset is 1458 observations and 123 variables.

As we are only concerned about the year 2016:
```{r}
hfi_2016 <- subset(hfi, year == 2016)
```

After selecting only the year 2016, we get that the dimension of the hfi_2016 is 162 obervation and 123 variables.

# 2. What type of plot would you use to display the relationship between the personal freedom score, pf_score, and pf_expression_control? #

I would use scatter plot to display the relationship between the pf_score and pf_expression_control as below:


```{r}
plot(hfi_2016$pf_score ~ hfi_2016$pf_expression_control,
     xlab = "Expression control", ylab = "Pf Score", col = "red")
```


# 3. Does the relationship look linear? If you knew a country’s pf_expression_control, or its score out of 10, with 0 being the most, of political pressures and controls on media content, would you be comfortable using a linear model to predict the personal freedom score? #

yes, I feel the relationship looks **linear** as with the increase in the expression control, the pf_score increases too. 

#Task 4: Sum of squared residuals #

# 4. Using openintro::plot_ss, choose a line that does a good job of minimizing the sum of squares. Run the function several times. What was the smallest sum of squares that you got? How does it compare to your neighbour’s? #

After running the sum of square multiple times, the smallest number of sum of square I got was 108.484


# Task 5: The Linear Model #

```{r}
m1 <- lm(pf_score ~ pf_expression_control, data = hfi_2016)
m1
tidy(m1)
```

```{r}
summary(m1)
```

# 5. Interpret the y - intercept #

The y-intercept is 4.2838. So, the human freedom score with no amount of political pressure on media is 4.2838. For countries with a pf_expression_control of 0 (those with the largest amount of political pressure on media content), we expect their mean personal freedom score to be 4.28

# 6. Interpret the slope # 

The slope here is 0.5419. So, for each additional amount of the pressure on media content score, we would see the human freedom score to increase by 0.5419. 

# Day 2- Assessing an SLR Model #

## 1. What does this value mean in the context of this mode ? ##



```{r}
hfi_2016 %>%
  group_by(pf_score, pf_expression_control)%>%
  summarize(cor = cor(pf_score, pf_expression_control))
```

```{r}
glance(m1)
```


## 2. What is the value of Rsquare for this model ? ##

The R square for this model is 0.7141.

## 3. What does this value mean in the context of this model? ##

This means that the model is 71.41% accurate.

## 4. 



```{r}
model <- lm(hf_score ~ pf_expression_control, data = hfi_2016)
```

```{r}
summary(model)
```

Equation of the Regression Line: 5.05340 + 0.36843

## Task 3: Prediction and Prediction Erros ##

```{r scatterplot}
ggplot(data = hfi_2016, aes(x = pf_expression_control, y = pf_score))+
  geom_point()
  stat_smooth(method= "lm", se = FALSE)
```

```{r rating of 3}
pf_expression_control <- 3

```

## 6. Predict a country's personal freedom school for one with 3 rating ##

```{r}
hfi_2016 %>%
  group_by(pf_score)%>%
  filter(pf_expression_control == 3)
```
## 7. Residual value for the prediction ##

```{r residual value}

standardres <- rstandard(model)
standardres

```


# Task 4: Model Diagnostics #

```{r}
m1_aug <- augment(m1)
```


```{r}
ggplot(data = m1_aug, aes(x = .fitted, y = .resid))+
  geom_point()+
  geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
  xlab("Fitted values") +
  ylab("Residuals")
```
We can see that there is no pattern in the residual so there is a relationship between two variables.


### Nearly Normal Residuals ###

```{r}
ggplot(data = m1_aug, aes(x= .resid))+
  geom_histogram(binwidth = 0.25)+
  xlab("Residuals")
  
```

We can also use QQ plot to see if the normality assumption has been violated:

```{r}
ggplot(data = m1_aug, aes(sample = .resid))+
  stat_qq()
```
I believe the nearly normal residual seems to be violated. As we can see in the beginning, the QQ plot doesn't follow a straight line at the begining which may violate the normal residual assumption.


### Constant Variablity ###

The points residuals and  fitted plot show that points are scattered around 0, there is a constant variability. So, it has not been violated. 

